### 2021-08-03 yfcc100m/paper/vldb2021/eval.tex
Update tex files for camera ready

We use the metadata associated with the images to filter the images.
We use the \textit{autotags} (as they contain information about the content
of the image), and geo-location information (latitude/longitude)
of the images for search and filtering.
Note that, even if we use geo-location for our study, any other property
assigned to the images can be used to refine the search
in both VDMS and baseline implementations.
On top of that, and for our use cases, we would like to extract more information
about the content of the image through the use of ML,
such as Convolutional Neural Networks~\cite{cnn}.
For this, we resize the images to 224x224, which is the input layer size for
popular variations of neural networks for object detection on images~\cite{resnet}.
We used both ResNet and Yolov3 for object detection, both of which
have the requirement of a downsized, lower resolution image as input.

@@

To analyze these results, one needs to compare the full-line (VDMS) versus the
dotted-lines (two baselines).
We start with a simple query that involves a simple
metadata filtering over 1 tag and also geo-location,
plus pre-processing operations.
Figure~\ref{fig:concurrency_comparison_q2} illustrates a concurrency analysis
for \textit{q2} (\textit{1tag\_geo\_resize}), described above,
using VDMS and the baselines.
Here we evaluate the concurrency of all systems, as the number of concurrent
clients grows (x-axis) and as the size of the databases grow.
Figure~\ref{fig:concurrency_comparison_q2} shows throughput (images per second)
when retrieving resized versions of the images, as the number of
concurrent clients increase.
The first thing to notice is that VDMS outperforms both baselines for all
databases for this query by a large margin.
For the baseline systems, in the case of 100M, the increase in the
size of data seems to have a larger impact in performance.
This result can be attributed to the increase in the complexity of the JOIN
operation as the number of rows in the tables increases.

>>>>

We use the metadata associated with the images to filter the images.
We use the \textit{autotags} (as they contain information about the content
of the image), and geo-location information (latitude and longitude)
of the images for search and filtering.
Note that, even if we use geo-location for our study, any other property
assigned to the images can be used to refine the search
in both VDMS and baseline implementations.
On top of that, and for our use cases, we would like to extract more information
about the content of the image through the use of ML,
such as Convolutional Neural Networks~\cite{cnn}.
For this, we resize the images to 224x224, which is the input layer size for
popular variations of neural networks for object detection on images~\cite{resnet}.
We used both ResNet and Yolov3 for object detection, both of which
have the requirement of a downsized, lower resolution image as input.

@@

To analyze these results, one needs to compare the full-line (VDMS) versus the
dotted-lines (two baselines).
We start with a simple query that involves a simple
metadata filtering over 1 tag and also geo-location,
plus pre-processing operations.
Figure~\ref{fig:concurrency_comparison_q2} illustrates a concurrency analysis
for \textit{q2} described above (\textit{1tag\_geo\_resize}),
using VDMS and the baselines.
Here we evaluate the concurrency of all systems, as the number of concurrent
clients grows (x-axis) and as the size of the databases grow.
Figure~\ref{fig:concurrency_comparison_q2} shows throughput (images per second)
when retrieving resized versions of the images, as the number of
concurrent clients increase.
The first thing to notice is that VDMS outperforms both baselines for all
databases for this query by a large margin.
For the baseline systems, in the case of 100M, the increase in the
size of data seems to have a larger impact in performance.
This result can be attributed to the increase in the complexity of the JOIN
operation as the number of rows in the tables increases.
